But I can't preregister my research: Improving the reproducibility and transparency of ecology and conservation with adaptive preregistration for model-based research

### 2024-09-22 _analysis/ms.qmd
Add gt table with quarto template items

>>>>

```{r}
#| label: tbl-preregistration-template-final
#| tbl-cap: "Final version of preregistation template developed after user-testing."

library(tidyverse)
library(gt)
prereg_tbl_data <- 
  readr::read_csv(
    here::here("outputs/quarto_preregistration_template.csv")
) %>% 
    drop_na(phase) %>% 
    nest(.by = phase) %>% 
    mutate(phase_id = row_number()) %>% 
    unnest(data) %>% 
    nest(.by = c(phase, 
                 step)) %>% 
    group_by(phase) %>%  
    mutate(step_id = row_number()) %>% 
    unnest(data) %>%  
    ungroup %>% 
    nest(.by = c(phase, 
                 step, 
                 substep)) %>% 
    group_by(phase, step) %>% 
    mutate(substep_id = row_number()) %>% 
    unnest(data) %>% 
    ungroup %>% 
    nest(.by = c(phase, 
                 step, 
                 substep, 
                 preregistration_item)) %>% 
    group_by(phase, step, substep) %>% 
    mutate(preregistration_item_id = row_number()) %>% 
    unnest(data) %>% ungroup %>% 
    nest(.by = c(phase, 
                 step, 
                 substep, 
                 preregistration_item, 
                 preregistration_subitem)) %>% 
    group_by(phase, step, substep, preregistration_item) %>% 
  mutate(preregistration_subitem_id = row_number()) %>% 
    unnest(data) %>% 
  ungroup %>%  
    mutate(preregistration_item = 
             case_when(preregistration_subitem_id != 1 ~ NA, 
                       .default = preregistration_item),) %>% 
    mutate(substep = 
             case_when(substep_id != row_number() ~ NA, 
                               .default = substep),
           substep_description = 
             case_when(substep_id != row_number() ~ NA, 
                       .default = substep_description), 
           .by = substep) %>% 
    mutate(step = 
             case_when(step_id != row_number() ~ NA, 
                            .default = step),
           step_description = 
             case_when(substep_id != row_number() ~ NA, 
                                        .default = step_description),
           .by = step)  %>% 
    mutate(across(everything(), ~ stringr::str_remove_all(.x, "\\*")),
           phase = gluedown::md_bold(phase),
           phase_description = gluedown::md_italic(phase_description),
           across(ends_with("_id"), as.numeric))

prereg_tbl_data %>% 
    select(starts_with("phase"), starts_with("step"), starts_with("substep"), ends_with("_item"), ends_with("subitem"), everything()) %>% 
    mutate(step = case_when(!is.na(step) ~ gluedown::md_bold(step), .default = step),
           step_description = case_when(!is.na(step_description) ~ gluedown::md_italic(step_description), .default = step_description)) %>% 
    gt::gt(groupname_col = c("phase", "phase_description"),
           row_group.sep = ": ") %>% 
    gt::cols_hide(ends_with("_id")) %>% 
    gt::sub_missing(missing_text = "") %>% 
    gt::text_transform(fn = function(x) map(x, gt::md), 
                       locations = gt::cells_row_groups()) %>% 
   gt::text_transform(fn = gt::md, 
                       locations = gt::cells_body()) %>% 
    gt::cols_merge(columns = c("step", "step_description"), pattern = "{1} {2}") %>% 
    gt::cols_merge(columns = c("substep", "substep_description"), pattern = "{1} {2}") 
```

gt
